Supporting Information: The Transport Mechanisms of Polar Solutes in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-03-18 Ben_Manuscripts/transport/Outline.tex
Updates to outline + supporting

  \subsection*{Dwell and Hop Length Distributions}\label{method:hops_and_dwells}

  %MRS1: we probably only want enough do identify mechanism not to fit anything.  Think about minimum needed for physical understanding.
  %BJC1: right, the following is the bear minimum if we want to mention dwell time and hop lengths at all. Otherwise this can be omitted.

  \noindent We measured the distribution of dwell times and hop lengths in order to test
  the hypothesis that solutes follow a CTRW process.
  \begin{itemize}
	\item We used the \texttt{ruptures} python package in order to identify
	breakpoints, times when hops occur, in solute trajectories.\cite{truong_ruptures:_2018}
%	(See Supporting Information for more details on chosen parameters. i.e. type of cost 
%	function, cost function penalty	tolerance, number of dimensions used)
	\item The corresponding hop lengths and dwell times between break points were 
	used to construct empirical distributions.
  \end{itemize}

@@

  We measured the average radial distance of each solute of interest from the pore
  centers.
  \begin{itemize}
	\item We binned the radial distances and then normalized by the volume
	of the annulus defined by the bin edges.
	\item Although the pores are often described as straight, they have a
	small degree of tortuosity which disrupts the RDF calcuation 
    % MRS1: can you report numerically the tortuosity?
	\item We tried to mitigate the effects of tortuosity by calculating the RDF
	with respect to splines that run through the pore centers.
	\item We construct the splines by dividing the membrane into 10 slices
	in the $z$-direction. Within each slice, we calculate the location of 
	the pore centers based on the average location of the aromatic rings
	that make up the monomer head groups.
	\item When calculating the RDF, the radial distance from the pore center
	is based on the distance between the solute center-of-mass and the linearly
	interpolated ($x$, $y$)	coordinates of the pore center calculated based
	on the spline.
  \end{itemize}

@@

  %MRS1: We want to be able to say that conclusions are independent of reasonable changes in the definition so
  %we are not picking and choosing results (either consciously or unconsciously) 
  Based on the geometric criteria proposed by Luzar and Chandler \cite{luzar_effect_1996},
  we determined a hydrogen bond to exist if the distance between the donor, D, and acceptor,
  A, atoms is less than 3.5 \AA~and the angle formed by D--H...A is less than 30\degree.
    %BJC: According to Luzar/Chandler: The range of a water molecule’s first coordination
    % shell is 3.5 Å, as determined from the oxygen-oxygen radial distribution function.
    % The amplitude of librations that break hydrogen bonds is ,~ 30 degrees, as estimated
    % from Debye-Waller factors
  \begin{itemize}
    \item Attempts to describe a hydrogen bond in the context of molecular simulations has
    yielded a number of definitions with no true consensus \cite{prada-gracia_quest_2013}.
	\item The geometry of hydrogen bonds has some dependence on the system being studied. 
    \item The definition of Luzar and Chandler is easily visualized for trajectories using
    the \texttt{hbonds} representation of the Visual Molecular Dynamics (VMD) software 
    package which allows us to directly check the validity of identified hydrogen bonds.
    \item We tested the sensitivity of our conclusions to this definition in 
    the Supporting Information.
    %BJC: might need to update this if something better exists for nitrogen 
  \end{itemize}

@@

  Using our procedure we found that sodium ions in a solution of tip3p water
  coordinate with an average of 3.4 water molecules.
  \begin{itemize}
    \item We created a 4 x 4 x 4 nm cubic box of water with the GROMACS tool,
    \texttt{gmx solvate}
    \item We used \texttt{gmx genion} to replace water molecules with sodium
    and chloride ions in order to create a 0.6 M NaCl solution.
    \item We let the system simulate for 5 ns and reported the average
    number of coordinated water molecules per frame after discarding the first ns of 
    simulation. % need to actually do this
    \item We found that the reported average value is not sensitive to NaCl
    concentration (See Supporting Information)
  \end{itemize}

@@

@@

  %BJC: I'm not sure if would be better to normalize the densities so that the
  % shape of the sodium density is more pronounced
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{component_density_5wt.pdf}
  \caption{5 wt\% water}\label{fig:component_density_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{component_density_10wt.pdf}
  \caption{10 wt\% water}\label{fig:component_density_10wt}
  \end{subfigure}
  %MRS1: explicitly state the normalization used for the RDF.
  %MRS1: possibly include vertical dotted line to show where max head group peak occurs.
  \caption{The radial densities of various monomer components paint a picture of the
  pore topology where the pore centers are primarily composed of water and sodium ions.
  The 5 wt \% system (a) appears to be much more crowded by monomers than the 
  10 wt \% system (b). Head groups in (a) are densest closer to the pore center than
  in (b). A small amount of tail components find their way close to the pore center 
  of the 5 wt \% system. }\label{fig:component_densities}
  \end{figure}

@@

  \noindent Sodium coordinates with far less water molecules than it does in 
  bulk solution.
  \begin{itemize}
    \item In our system, on average, each sodium ion is coordinated to about 1.7 
    water molecules in the 10 wt \% system and 1.15 water molecules in the 5 wt\% 
    system.
    \item The low levels of water coordination under confinement are likely driven
    in part by favorable interactions between sodium ions and carboxylate head groups.
    \item A dehydrated sodium ion is not shielded from the negatively charged 
    carboxylate group.~\cite{ma_drastically_2019}
    %MRS1: are ``head group oxygen'' atoms the same as carboxylate? Not clear. 
    \item On average, sodium ions coordinate with 0.5 head group oxygen atoms in the
    10 wt \% water system and 0.4 head group oxygen atoms in the 5 wt \% water system. 
    % BJC: I thought 5 wt \% might be a little higher. These numbers might be skewed by
    % sodium ions that are within cutoff of both carboxylate oxygen atoms. Might be
    % better to report average number of sodiums coordinated to a head group
  \end{itemize}

  % BJC: This figure is from methanol simulations. Will be replaced by pure water
  % simulations
  % BJC: I can probably just report the averages rather than plot this
  %MRS1: yeah, this is not really worth a graphic.
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{Na_water_coordination.pdf}
  \caption{}\label{fig:na_water_coordination}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{Na_hg_coordination.pdf}
  \caption{}\label{fig:na_hg_coordination}  % No caption since this probably won't be a figure
  \end{subfigure}
  \end{figure}

@@

  \noindent The MSDs are not a monotonic function of solute size.
  \begin{itemize}
  	\item We plotted the solute size against their MSDs in Figure~\ref{fig:msd_radius_5wt} and~\ref{fig:msd_radius_10wt}.
  	\item There are numerous examples of solutes in our study that do not 
  	follow the behavior set forth by the Stokes-Einstein equation which 
  	implies that solute MSD should be inversely related to solute size.  % citation
        %MRS1: can you plot on the figure what the relatioship SHOULD look like?  It sort of looks linear-ish (especially 5).
  	\item This behavior is not entirely surprising but worth emphasizing. 
  	\item It is expected that the Stokes-Einstein relationship, which assumes that 
  	the solute radius is much larger than the solvent, should break down once
  	solute and solvent are of comparable size.
        %MRS1: these points below seem more like intro points.

  	\item Membranes, including that studied here, are often characterized 
  	with size-exclusion experiments which emphasizes selectivity based on the ability
  	to enter a given pore. 
  	\item Once we reach the nm to sub-nm pore size regime, size-exclusion 
  	becomes of secondary importance since the primary purpose of these membranes is to 
  	separate molecules whose sizes are on the same order as water.
  	\item In order to handle complex waste streams with molecules of similar size,
  	it is important to take advantage of material properties other than pore size. 
%  	\item Tetrose, our fifth largest solute, has an average MSD higher than more 
%  	than half of all solutes studied. 
%  	\item The two slowest solutes, DMF and THF, are smaller than 10 faster solutes.
%  	\item Transport is clearly affected by factors other than molecular size. 
  \end{itemize}

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_5wt_tamsds.pdf}
  \caption{5 wt \% water}\label{fig:all_msds_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_10wt_tamsds.pdf}
  \caption{10 wt \% water}\label{fig:all_msds_10wt}
  \end{subfigure}
  %BJC: missing a few since those simulations just got started
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_5wt.pdf} 
  \caption{5 wt \% water}\label{fig:msd_radius_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_10wt.pdf} 
  \caption{10 wt \% water}\label{fig:msd_radius_10wt}
  \end{subfigure}
  \caption{The MSDs of solutes in the 5 wt \% water system (a) are significantly
  smaller than those of the solutes in the 10 wt \% water system (b). The
  MSDs are not a monotonic function of molecular size (c and d).}\label{fig:msds}
  \end{figure}  
  %MRS1: Having so much data here grapically is nice.  ought to think how else data can be displayed. Perhaps figures with the dwell times as well?  Depends on if those are being shown.  2D scatter plots with average partitioning distance of solute vs. MSD? We should keep brainstorming which will be most relevant. 
  \noindent On the timescales simulated in our study, solutes exhibit subdiffusive behavior.
  %, providing the beginnings of an answer to question~\ref{question:mechanisms}.
  \begin{itemize}  
    \item Figure~\ref{fig:example_ztraces} plots the $z$-coordinate versus time of
  	3 representative ethanol centers of mass in the 10 wt \% water system.
  	\item There are clear periods of entrapment separated by relatively large hops.
	\item The MSD calculated based on all ethanol molecules is plotted in 
	Figure~\ref{fig:example_msd} and is sublinear.
	\item The long periods of entrapment likely lead to this sublinear, and thus
	subdiffusive, behavior.
  \end{itemize}

>>>>

%  \subsection*{Dwell and Hop Length Distributions}\label{method:hops_and_dwells}
%
%  %MRS1: we probably only want enough do identify mechanism not to fit anything.  Think about minimum needed for physical understanding.
%  %BJC1: right, the following is the bear minimum if we want to mention dwell time and hop lengths at all. Otherwise this can be omitted.
%
%  \noindent We measured the distribution of dwell times and hop lengths in order to test
%  the hypothesis that solutes follow a CTRW process.
%  \begin{itemize}
%	\item We used the \texttt{ruptures} python package in order to identify
%	breakpoints, times when hops occur, in solute trajectories.\cite{truong_ruptures:_2018}
%%	(See Supporting Information for more details on chosen parameters. i.e. type of cost 
%%	function, cost function penalty	tolerance, number of dimensions used)
%	\item The corresponding hop lengths and dwell times between break points were 
%	used to construct empirical distributions.
%  \end{itemize}

  \subsection*{The Stokes-Einstein Relationship}\label{method:stokes}

  The Stokes-Einstein relationship expresses the diffusion coefficient of 
  a hard spherical particle as a function inversely related to its radius.
  \begin{itemize}
  	\item $D = \dfrac{k_bT}{6\pi\eta r}$ where $k_b$ and $T$ are Boltzmann
  	constant and the system temperature respectively and $\eta$ is the 
  	system's viscosity.
  	\item For calculation relevant to this study, we assume that the viscosity
  	is constant.
  	\item Additionally, we will apply the relationship to solute MSDs which is
  	valid because all trajectories are of the same length.
  	\item It is well-known that the relationship breaks down when solute size becomes
  	on the order of solvent size because the solute can no longer be treated
  	as a non-interacting hard sphere. 
  \end{itemize}

  Gierer and Wirtz introduced a microfriction correction factor in order to 
  address this issue. 
  \begin{itemize}
    \item They proposed that $D = \dfrac{k_bT}{6\pi\eta fr}$
    %\item Where $f = \left(1.5\dfrac{r_2}{r_1} + \dfrac{1}{1 + \dfrac{r_2}{r_1}}\right)^{-1}$
    \item Where $f = \left(1.5(r_2/r_1) + \dfrac{1}{1 + (r_2/r_1)}\right)^{-1}$
    \item and $r_1$ and $r_2$ are the radii of the solute and solvent molecules
    respectively.
  \end{itemize}

@@

  We measured the average radial distance of each solute of interest from the pore
  centers.
  \begin{itemize}
	\item We binned the radial distances and then normalized by the volume
	of the annulus defined by the bin edges.
	\item Although the pores are often described as straight, they have a
	small degree of tortuosity which disrupts the RDF calcuation.
    % MRS1: can you report numerically the tortuosity?
    % BJC1: added at end of paragraph after introduction of splines since tortuosity calculation uses splines.
	\item We tried to mitigate the effects of tortuosity by calculating the RDF
	with respect to splines that run through the pore centers.
%    \item We construct the splines by dividing the membrane into 10 slices
%	in the $z$-direction. Within each slice, we calculate the location of 
%	the pore centers based on the average location of the aromatic rings
%	that make up the monomer head groups.
	\item Each spline consists of 10 points, equally spaced in the $z$-direction, whose
    ($x$, $y$) coordinates are defined based on the center of mass of all head
    groups closest, in $z$, to the given point.
	\item When calculating RDFs, the radial distance from the pore center
	is based on the distance between the solute center-of-mass and the linearly
	interpolated ($x$, $y$)	coordinates of the pore center calculated based
	on the spline.
	\item Using the splines, we calculated the tortuosity of the 
	pores by calculating the ratio $\dfrac{L}{Z}$ where $L$ is the length of the spline and $Z$ is 
    the length of the unit cell in the $z$-direction. 
    \item The average tortuosity of each pore is 1.03 $\pm$ 0.01 and 1.07 $\pm$ 0.02 in the 
    5 and 10 wt \% systems respectively. 
%    \item Although the value of tortuosity is low, the author's experience suggests
%    that a spline is still justified.	
  \end{itemize}

@@

  %MRS1: We want to be able to say that conclusions are independent of reasonable changes in the definition so
  %we are not picking and choosing results (either consciously or unconsciously) 
  Based on the geometric criteria proposed by Luzar and Chandler \cite{luzar_effect_1996},
  we determined a hydrogen bond to exist if the distance between the donor, D, and acceptor,
  A, atoms is less than 3.5 \AA~and the angle formed by D--H...A is less than 30\degree.
    %BJC: According to Luzar/Chandler: The range of a water molecule’s first coordination
    % shell is 3.5 Å, as determined from the oxygen-oxygen radial distribution function.
    % The amplitude of librations that break hydrogen bonds is ,~ 30 degrees, as estimated
    % from Debye-Waller factors
  \begin{itemize}
    \item Attempts to describe a hydrogen bond in the context of molecular simulations has
    yielded a number of definitions with no true consensus \cite{prada-gracia_quest_2013}.
	\item The geometry of hydrogen bonds has some dependence on the system being studied. 
    \item The definition of Luzar and Chandler is easily visualized for trajectories using
    the \texttt{hbonds} representation of the Visual Molecular Dynamics (VMD) software 
    package which allows us to directly check the validity of identified hydrogen bonds.
    \item We tested the sensitivity of our conclusions to this definition in 
    Section~\ref{S-section:hbond_sensitivity} of the SI.
    %BJC: might need to update this if something better exists for nitrogen 
  \end{itemize}

@@

  Using our procedure we found that sodium ions in a solution of tip3p water
  coordinate with an average of 3.4 water molecules.
  \begin{itemize}
    \item We created a 4 x 4 x 4 nm cubic box of water with the GROMACS tool,
    \texttt{gmx solvate}
    \item We used \texttt{gmx genion} to replace water molecules with sodium
    and chloride ions in order to create a 0.6 M NaCl solution.
    \item We let the system simulate for 5 ns and reported the average
    number of coordinated water molecules per frame after discarding the first ns of 
    simulation. % need to actually do this
    \item We found that the reported average value is not sensitive to NaCl
    concentration (See section~\ref{S-section:coord_number} of the SI)
  \end{itemize}

@@

  Before beginning the analysis of transport behavior, it is important to elucidate
  the topology of the membrane pores.

@@

  % BJC1: Should I show a dry system?
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.415\textwidth}
  \includegraphics[width=\textwidth]{component_density_5wt.pdf}
  \caption{5 wt\% water}\label{fig:component_density_5wt}
  \end{subfigure}
  \begin{subfigure}{0.15\textwidth}
  \vspace{-0.5cm}
  \includegraphics[width=\textwidth]{monomer_color_coded.pdf}
  \label{fig:monomer_color_coded}
  \end{subfigure}
  \begin{subfigure}{0.415\textwidth}
  \includegraphics[width=\textwidth]{component_density_10wt.pdf}
  \caption{10 wt\% water}\label{fig:component_density_10wt}
  \end{subfigure}

  %MRS1: possibly include vertical dotted line to show where max head group peak occurs.
  %BJC1: tried it out. Seems like a good addition.
  \caption{The radial densities of various monomer components paint a picture of the
  pore topology where the pore centers are primarily composed of water and sodium ions.
  All RDFs represent the number of atoms located at a given distance from the pore center
  normalized by the volume of the annular bin 
  to which they belong. The 5 wt \% system (a) appears to be much more crowded by monomers
  than the 10 wt \% system (b). Head groups in (a) are densest about 0.2 nm closer to the
  pore center than in (b). A small amount of tail components find their way close to the 
  pore center of the 5 wt \% system.
  }\label{fig:component_densities}
  \end{figure}

@@

  \noindent Sodium coordinates with far less water molecules than it does in 
  bulk solution.
  \begin{itemize}
    \item Compared to 3.4 coordinated water molecules in bulk solution (see 
    section~\ref{method:coordination}), sodium ions in our system are, on average,
    coordinated to about 1.7 water molecules in the 10 wt \% system and 1.2 water
    molecules in the 5 wt\% system.
    \item The low levels of water coordination under confinement are likely driven
    in part by favorable interactions between sodium ions and carboxylate head groups.
    \item A dehydrated sodium ion is not shielded from the negatively charged 
    carboxylate group.~\cite{ma_drastically_2019}. 
    \item On average, sodium ions coordinate with 0.5 carboxylate group oxygen atoms in the
    10 wt \% water system and 0.4 carboxylate oxygen atoms in the 5 wt \% water system. 
    % BJC: I thought 5 wt \% might be a little higher. These numbers might be skewed by
    % sodium ions that are within cutoff of both carboxylate oxygen atoms. Might be
    % better to report average number of sodiums coordinated to a head group
  \end{itemize}

  % BJC: This figure is from methanol simulations. Will be replaced by pure water
  % simulations
  % BJC: I can probably just report the averages rather than plot this
  %MRS1: yeah, this is not really worth a graphic.
%  \begin{figure}[!htb]
%  \centering
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{Na_water_coordination.pdf}
%  \caption{}\label{fig:na_water_coordination}
%  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{Na_hg_coordination.pdf}
%  \caption{}\label{fig:na_hg_coordination}  % No caption since this probably won't be a figure
%  \end{subfigure}
%  \end{figure}

@@

  \noindent The MSDs are not a monotonic function of solute size.
  \begin{itemize}
  	\item We plotted the solute size against their MSDs in Figure~\ref{fig:msd_radius_5wt}
  	and~\ref{fig:msd_radius_10wt}.
  	\item Based on the Stokes-Einstein relationship, it is expected that
  	the solute MSDs should be inversely related to solute size.
  	\item Once solute and solvent are of comparable size, the relationship breaks
  	down and tends to underestimate the MSD. 
  	\item Gierer and Wirtz introduced a microfriction factor as theoretical
  	correction.
%  	\item It is expected that the Stokes-Einstein relationship, which assumes that 
%  	the solute radius is much larger than the solvent, should break down once
%  	solute and solvent are of comparable size.
  	\item Assuming that the Stokes-Einstein relationship is no longer valid 
  	for solutes with radius less than x nm, we fit the Stokes-Einstein relationship 
  	with and without the correction factor making sure that the two curves intersected
  	at x nm and that the corrected line passed through the highest MSD data point, methanol. %BJC1: need a justified value for x. Can also show its insensitivity to choice of intersection point.
  	\item We believe methanol is subject to the least hindrance due to its 
  	size 
  	\item Although both curves are approximations, they illustrate that
  	the majority of solutes in our study show lower than expected MSDs. 
%  	\item There are numerous examples of solutes in our study that do not 
%  	follow the behavior set forth by the Stokes-Einstein equation which 
%  	implies that solute MSD should be inversely related to solute size.  % citation
%    % MRS1: can you plot on the figure what the relatioship SHOULD look like?  It sort of looks linear-ish (especially 5).
%  	\item This behavior is not entirely surprising but worth emphasizing. 
	%BJC1: below moved to intro
%  	\item Membranes, including that studied here, are often characterized 
%  	with size-exclusion experiments which emphasizes selectivity based on the ability
%  	to enter a given pore. 
%  	\item Once we reach the nm to sub-nm pore size regime, size-exclusion 
%  	becomes of secondary importance since the primary purpose of these membranes is to 
%  	separate molecules whose sizes are on the same order as water.
%  	\item In order to handle complex waste streams with molecules of similar size,
%  	it is important to take advantage of material properties other than pore size. 
%  	\item Tetrose, our fifth largest solute, has an average MSD higher than more 
%  	than half of all solutes studied. 
%  	\item The two slowest solutes, DMF and THF, are smaller than 10 faster solutes.
%  	\item Transport is clearly affected by factors other than molecular size. 
  \end{itemize}

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_5wt_tamsds.pdf}
  \caption{5 wt \% water}\label{fig:all_msds_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_10wt_tamsds.pdf}
  \caption{10 wt \% water}\label{fig:all_msds_10wt}
  \end{subfigure}
  %BJC: missing a few since those simulations just got started
  %BJC1: wondering if I should add some kind of confidence interval to the Stoke-Einstein plots. Based on the errorbars of methanol
  %BJC1: should the points be labeled with residue names?
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_5wt.pdf} 
  \caption{5 wt \% water}\label{fig:msd_radius_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_10wt.pdf} 
  \caption{10 wt \% water}\label{fig:msd_radius_10wt}
  \end{subfigure}
  \caption{The MSDs of solutes in the 5 wt \% water system (a) are significantly
  smaller than those of the solutes in the 10 wt \% water system (b). The
  MSDs are not a monotonic function of molecular size (c and d). A significant
  number of solute MSDs fall below the theoretical lines predicted by the 
  Stokes-Einstein equation and Gierer and Wirtz' corrected Stokes-Einstein equation.}\label{fig:msds}
  \end{figure}  
  %MRS1: Having so much data here grapically is nice.  ought to think how else data can be displayed. Perhaps figures with the dwell times as well?  Depends on if those are being shown.  2D scatter plots with average partitioning distance of solute vs. MSD? We should keep brainstorming which will be most relevant. 
  \noindent On the timescales simulated in our study, solutes exhibit subdiffusive behavior.
  %, providing the beginnings of an answer to question~\ref{question:mechanisms}.
  \begin{itemize}  
    \item Figure~\ref{fig:example_ztraces} plots the $z$-coordinate versus time of
  	3 representative ethanol centers of mass in the 10 wt \% water system.
  	\item There are clear periods of entrapment separated by relatively large hops.
	\item The MSD calculated based on all ethanol molecules is plotted in 
	Figure~\ref{fig:example_msd} and is sublinear.
	\item The long periods of entrapment likely lead to this sublinear, and thus
	subdiffusive, behavior.
  \end{itemize}

  % Stokes-Einstein underestimates diffusion coefficient for small molecules.
  % r down, f down, D up
  % Stokes-Einstein breaks down for particles less ___ nm in size
  % Fit corrected line through methanol.
  % Make stokes einstein intersect corrected line at breakdown radius

### 2019-03-18 Ben_Manuscripts/transport/Supporting_Information.tex
Updates to outline + supporting

>>>>

  \subsection{Pore Splines}\label{section:splines}

  We captured the apparent $z$-dependence of the pore center locations by
  constructing splines running through each pore (See Figure~\ref{fig:spline}).
  Each spline consists of 10 points, equally spaced in the $z$-direction, whose
  ($x$, $y$) coordinates are defined based on the center of mass of all head
  groups closest, in $z$, to the given point.

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=0.45\textwidth]{spline.pdf}
  \caption{We traced the center of each pore as a function of $z$ using a spline (pink
  line). We constructed the spline in each pore using 10 points (pink spheres) whose
  positions we defined based on the center of mass of the head groups in closest proximity
  to the spline point in the $z$-direction.}\label{fig:spline}
  \end{figure}

  We calculated the tortuosity, $\tau$, of the pores by calculating the 
  ratio $\dfrac{L}{Z}$ where $L$ is the length of the spline and $Z$ is 
  the length of the unit cell in the $z$-direction.
